Evaluation

### 2018-02-16 evaluation.Rmd
Assorted fixes, render site

# Setup rodent observations
species_abundance = portalr::abundance(shape='flat', level='Controls') %>%
  rename(actual = abundance) %>%
  mutate(level='Controls',currency='abundance') %>%
  left_join(new_moons, by='period') %>%
  filter(species %in% species_of_interest)

total_abundance = portalr::abundance(shape='flat', level='Controls') %>%
  group_by(period) %>%
  summarise(actual=sum(abundance)) %>%
  ungroup() %>%
  mutate(level='Controls',currency='abundance',species='total') %>%
  left_join(new_moons, by='period')

observation_data = species_abundance %>%
  bind_rows(total_abundance)

@@

##################################
#Combine forecasts and oservations
forecast_errors = forecast_data %>%
  left_join(observation_data, by=c('species','level','currency','newmoonnumber')) %>% 
  mutate(rmse = sqrt((estimate - actual)^2))

>>>>

# Setup rodent observations
species_abundance = portalr::abundance("repo", shape='flat', level='treatment', 
                                       length="longterm", time='newmoon') %>%
  filter(treatment=="control") %>%
  rename(actual = abundance, level = treatment) %>%
  mutate(level='Controls',currency='abundance') %>%
  filter(species %in% species_of_interest)

total_abundance = portalr::abundance("repo", shape='flat', level='treatment', 
                                     length="longterm", time='newmoon') %>%
  filter(treatment=="control") %>%
  group_by(newmoonnumber) %>%
  summarise(actual=sum(abundance)) %>%
  ungroup() %>%
  mutate(level='Controls',currency='abundance',species='total')

observation_data = species_abundance %>%
  bind_rows(total_abundance) %>% 
  left_join(new_moons, by='newmoonnumber')

@@

##################################
#Combine forecasts and oservations
forecast_errors = forecast_data %>%
  left_join(observation_data, by=c('newmoonnumber','level','species','currency')) %>% 
  mutate(rmse = sqrt((estimate - actual)^2))
